SubsidyExplorer - Step 10: Exploring high seas vessels

### 2022-09-30 scripts/10_high_seas_vessel_breakdown.Rmd
hs breakdowns, updated methodology, and database

```{r}
# # Load country dependencies helper file
# country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
#    mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
#                                   iso3 == "ANT" ~ "Netherlands Antilles",
#                                   iso3 == "ASC" ~ "Ascension Island", 
#                                   iso3 == "CPT" ~ "Clipperton Island",
#                                   iso3 == "TAA" ~ "Tristan da Cunha",
#                                   TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
#   arrange(sovereign_iso3) 
# 
# # Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
# wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
```

@@

```{r}
hs_vessel_dat <- vessel_dat_raw %>%
  dplyr::filter(prop_fishing_KWh_high_seas >= 0.05)

```

@@

```{r}
gear_type_breakdown <- hs_vessel_dat %>%
  group_by(vessel_class) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

@@

ggsave(paste0(results_dir, "hs_gear_type_breakdown.png"), gear_type_breakdown_plot, width = 7.5, height = 6)
```

@@

```{r}
length_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(length_m, seq(min(length_m), max(length_m) + 10, 10))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

@@

ggsave(paste0(results_dir, "hs_length_breakdown.png"), length_breakdown_plot, width = 7.5, height = 6)
```
## Tonnage breakdown

```{r}
tonnage_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(tonnage_gt, seq(min(tonnage_gt), max(tonnage_gt) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

@@

ggsave(paste0(results_dir, "hs_tonnage_breakdown.png"), tonnage_breakdown_plot, width = 7.5, height = 8)
```

@@

```{r}
engine_power_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(engine_power_kw, seq(min(engine_power_kw), max(engine_power_kw) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

@@

ggsave(paste0(results_dir, "hs_engine_power_breakdown.png"), engine_power_breakdown_plot, width = 7.5, height = 8)
```

>>>>

```{r}
# Load country dependencies helper file
country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
   mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
                                  iso3 == "ANT" ~ "Netherlands Antilles",
                                  iso3 == "ASC" ~ "Ascension Island",
                                  iso3 == "CPT" ~ "Clipperton Island",
                                  iso3 == "TAA" ~ "Tristan da Cunha",
                                  TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
  arrange(sovereign_iso3)

# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
```

@@

```{r}
hs_vessel_dat <- vessel_dat_raw %>%
  dplyr::filter(prop_fishing_KWh_high_seas >= 0.05)
```

@@

```{r}
gear_type_breakdown <- hs_vessel_dat %>%
  group_by(vessel_class) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T),
            n_vessels = n_distinct(ssvid))

@@

write_csv(gear_type_breakdown, paste0(results_dir, "hs_gear_type_breakdown.csv"))
ggsave(paste0(results_dir, "hs_gear_type_breakdown.png"), gear_type_breakdown_plot, width = 7.5, height = 6)
```

@@

```{r}
length_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(length_m, seq(min(length_m), max(length_m) + 10, 10))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T),
            n_vessels = n_distinct(ssvid))

@@

write_csv(length_breakdown, paste0(results_dir, "hs_length_breakdown.csv"))
ggsave(paste0(results_dir, "hs_length_breakdown.png"), length_breakdown_plot, width = 7.5, height = 6)
```

## Tonnage breakdown

```{r}
tonnage_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(tonnage_gt, seq(min(tonnage_gt), max(tonnage_gt) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T),
            n_vessels = n_distinct(ssvid))

@@

write_csv(tonnage_breakdown, paste0(results_dir, "hs_tonnage_breakdown.csv"))
ggsave(paste0(results_dir, "hs_tonnage_breakdown.png"), tonnage_breakdown_plot, width = 7.5, height = 8)
```

@@

```{r}
engine_power_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(engine_power_kw, seq(min(engine_power_kw), max(engine_power_kw) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T),
            n_vessels = n_distinct(ssvid))

@@

write_csv(engine_power_breakdown, paste0(results_dir, "hs_engine_power_breakdown.csv"))
ggsave(paste0(results_dir, "hs_engine_power_breakdown.png"), engine_power_breakdown_plot, width = 7.5, height = 8)
```
